### 2020-03-30 06-examples.tex
examples + flat fucntion

Sys  \defeq \ \restrict{r1,r2,r3,r4,\tilde{q},\tilde{w},\tilde{a},\tilde{b}} (P_q \mid \overline{P}_w  \mid  P_a  \mid \overline{P}_b  \mid  P_1  \mid  P_2  \mid  P_3  \mid P_4  \mid Cxt).

@@

\restrict{r1,r2,r3,r4,\tilde{q},\tilde{w},\tilde{a},\tilde{b}}\\
 (\startchain{\silent}\chainedlink{\overline{a}_i}{\bf  \overline{a}_i}\chainedlink{\bf \overline{a}_o}{\overline{a}_o}\chainedlink{r_2}{r_2}\chainedlink{q_i}{\bf q_i}\chainedlink{\bf q_i}{q_i}\chainedlink{b_i}{\bf b_i}\chainedlink{\bf b_i}{b_i}\chainedlink{\overline{w}_i}{\bf \overline{w}_i}\chainedlink{\bf \overline{w}_o}{\overline{w}_o}\chainedlink{\overline{a}_i}{\bf \overline{a}_i}\chainedlink{\bf \overline{a}_o}{\overline{a}_o}\chainedlink{r_3}{r_3}\chainedlink{\overline{a}_i}{\bf \overline{a}_i}\chainedlink{\bf \overline{a}_o}{\overline{a}_o}\chainedlink{r_4}{r_4}\chainedlink{\overline{w}_i}{\bf \overline{w}_i}\chainedlink{\bf \overline{w}_o}{\overline{w}_o}\chainedlink{cxt}{cxt}\chainedlink{\hat{a}_i}{\bf \hat{a}_i}\chainedlink{\bf \hat{a}_o}{\hat{a}_o}\chainedlink{\underline{b}_i}{\bf \underline{b}_i}\chainedlink{\bf \underline{b}_o}{\underline{b}_o}\chainedlink{p_1}{p_1}\chainedlink{p_2}{p_2}\chainedlink{\tilde{w}_i}{\bf \tilde{w}_i}\chainedlink{\bf \tilde{w}_o}{\tilde{w}_o}\chainedlink{p_3}{p_3}\chainedlink{p_4}{p_4}\chainend{\silent})

@@

\subsection{A  biological toy example}
Here we consider a biological toy example where a gene $a$  codes for a protein $T$ when molecules 
$G$ is present and $C$ is absent, and in the opposite situation $a$ codes for protein $T'$.
This behavior is encoded in rules $1$ and $2$.
Then, rule three codes for the production of $C$ when proteins $T$ and $F$ are present, and $T'$ absent;
rule four codes for the production of $G$ when  proteins $T'$ is present and $F$ is absent.
\paragraph{Encoding of the rules.}
The encoding of the rules for reactions is  given in a parametric way:
\[
\begin{array}{lcl}
P_n(a,G,C,T) & \defeq &\startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}
                                                    \chainedlink{G_i}{\noact}\chainedlink{\noact}{G_o}
                                                     \chainedlink{\overline{C}_i}{\noact}\chainedlink{\noact}{\overline{C}_o}
					        \chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}
					        \chainedlink{\tilde{T}_i}{\noact}\chainedlink{\noact}{\tilde{T}_o}
			\chainend{p_{n+1}}.P_n(a,G,C,T)  \\
				&& +\\
			&&P_n'(\overline{a}) \ +\ P_n'(\overline{G}) \ + \ P_n'(C)\\
			\end{array}
			\]
			\noindent
			where
			\[
\begin{array}{lcl}
P_n'(C) &\defeq &  \startchain{r_n}\chainedlink{C_i}{\noact}\chainedlink{\noact}{C_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n'(C) 
% \ + \   \startchain{r_n}\chainedlink{w_i}{\noact}\chainedlink{\noact}{w_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) \\
%			&&+\\
%			&& \startchain{r_n}\chainedlink{\overline{b}_i}{\noact}\chainedlink{\noact}{\overline{b}_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}\chainend{p_{n+1}}.P_n(q,b,w,a,q) \ + \  \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) 
\end{array}
\]

@@

Now, to show a possible composition of a transition label, we assume an system where the entities $a$, $T'$, and $G$ are present:
\[
\begin{array}{lcl}
Sys &\defeq &\restrict{\tilde{C},\tilde{G},\tilde{F}, \tilde{T},\tilde{T'}}( P_a\mid P_C\mid P_G\mid \overline{P}_F \mid \overline{P}_T \mid P_{T'} \mid P_1 \mid P_2 \mid P_3 \mid P_4)
\end{array}
\]
In the above configuration, reactions $1$ and $3$ can be applied, and also we assume that the context will provide the entity $F$, that will be available in the target configuration.
The transition label of

>>>>

Sys  \defeq \ %\restrict{r1,r2,r3,r4,\tilde{q},\tilde{w},\tilde{a},\tilde{b}}
 P_q \mid \overline{P}_w  \mid  P_a  \mid \overline{P}_b  \mid  P_1  \mid  P_2  \mid  P_3  \mid P_4  \mid Cxt.

@@

%\restrict{r1,r2,r3,r4,\tilde{q},\tilde{w},\tilde{a},\tilde{b}}\\
 \startchain{\silent}\chainedlink{\overline{a}_i}{\bf  \overline{a}_i}\chainedlink{\bf \overline{a}_o}{\overline{a}_o}\chainedlink{r_2}{r_2}\chainedlink{q_i}{\bf q_i}\chainedlink{\bf q_i}{q_i}\chainedlink{b_i}{\bf b_i}\chainedlink{\bf b_i}{b_i}\chainedlink{\overline{w}_i}{\bf \overline{w}_i}\chainedlink{\bf \overline{w}_o}{\overline{w}_o}\chainedlink{\overline{a}_i}{\bf \overline{a}_i}\chainedlink{\bf \overline{a}_o}{\overline{a}_o}\chainedlink{r_3}{r_3}\chainedlink{\overline{a}_i}{\bf \overline{a}_i}\chainedlink{\bf \overline{a}_o}{\overline{a}_o}\chainedlink{r_4}{r_4}\chainedlink{\overline{w}_i}{\bf \overline{w}_i}\chainedlink{\bf \overline{w}_o}{\overline{w}_o}\chainedlink{cxt}{cxt}\chainedlink{\hat{a}_i}{\bf \hat{a}_i}\chainedlink{\bf \hat{a}_o}{\hat{a}_o}\chainedlink{\underline{b}_i}{\bf \underline{b}_i}\chainedlink{\bf \underline{b}_o}{\underline{b}_o}\chainedlink{p_1}{p_1}\chainedlink{p_2}{p_2}\chainedlink{\tilde{w}_i}{\bf \tilde{w}_i}\chainedlink{\bf \tilde{w}_o}{\tilde{w}_o}\chainedlink{p_3}{p_3}\chainedlink{p_4}{p_4}\chainend{\silent}

@@

\subsection{A  biological toy example}\label{subsec:toy}
Hereafter, we only take into account transitions whose labels are solid, i.e. they do not contain 
virtual links, and   complete, i.e. thy starts and ends with the $\silent$ symbol.\\

Here we consider a biological toy example where a gene $a$  codes for a protein $T$ when molecules 
$G$ is present and $C$ is absent, and in the opposite situation $a$ codes for protein $T'$.
This behavior is encoded in rules $1$ and $2$.
Then, rule three codes for the production of $C$ when proteins $T$ and $F$ are present, and $T'$ absent;
rule four codes for the production of $G$ when  proteins $T'$ is present and $F$ is absent.
\paragraph{Encoding of the rules.}
The encoding of the rules for reactions is  given in a parametric way:
\[
\begin{array}{lcl}
P_n(a,G,C,T) & \defeq &\startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}
                                                    \chainedlink{G_i}{\noact}\chainedlink{\noact}{G_o}
                                                     \chainedlink{\overline{C}_i}{\noact}\chainedlink{\noact}{\overline{C}_o}
					        \chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}
					        \chainedlink{\tilde{T}_i}{\noact}\chainedlink{\noact}{\tilde{T}_o}
			\chainend{p_{n+1}}.P_n(a,G,C,T)  \\
				&& +\\
			&&P_n'(\overline{a}) \ +\ P_n'(\overline{G}) \ + \ P_n'(C)\\
			\end{array}
			\]
			\noindent
			where
			\[
\begin{array}{lcl}
P_n'(C) &\defeq &  \startchain{r_n}\chainedlink{C_i}{\noact}\chainedlink{\noact}{C_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n'(C) 
% \ + \   \startchain{r_n}\chainedlink{w_i}{\noact}\chainedlink{\noact}{w_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) \\
%			&&+\\
%			&& \startchain{r_n}\chainedlink{\overline{b}_i}{\noact}\chainedlink{\noact}{\overline{b}_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}\chainend{p_{n+1}}.P_n(q,b,w,a,q) \ + \  \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) 
\end{array}
\]

@@

Now, to show a possible composition of a transition label, we assume an system where the entities $a$, $T'$, and $G$ are present:
\[
\begin{array}{lcl}
Sys &\defeq &%\restrict{\tilde{C},\tilde{G},\tilde{F}, \tilde{T},\tilde{T'}}(
P_a\mid \overline{P}_C\mid P_G\mid \overline{P}_F \mid \overline{P}_T \mid P_{T'} \mid P_1 \mid P_2 \mid P_3 \mid P_4
\end{array}
\]
In the above configuration, reactions $1$ and $3$ can be applied, and also we assume that the context will provide the entity $F$, that will be available in the target configuration.
The transition label appears as:
\[
\tiny
\begin{array}{l}
%\restrict{r1,r2,r3,r4,a,\tilde{C},\tilde{G},\tilde{F},\tilde{T},\tilde{T'}}\\
 \startchain{\silent}\chainedlink{a_i}{\bf  a_i}\chainedlink{\bf a_o}{a_o}
 \chainedlink{G_i}{\bf  G_i}\chainedlink{\bf G_o}{G_o}
 \chainedlink{\overline{C}_i}{\bf \overline{C}_i}\chainedlink{\bf \overline{C}_o}{\overline{C}_o}
 \chainedlink{r_2}{r_2}\chainedlink{G_i}{\bf G_i}\chainedlink{\bf G_o}{G_o}
\chainedlink{r_3}{r_3}\chainedlink{T'_i}{\bf T'_i}\chainedlink{\bf T'_o}{T'_o}\chainedlink{r_4}{r_4}\chainedlink{T'_i}{\bf T'_i}\chainedlink{\bf T'_o}{T'_o}\chainedlink{\overline{F}_i}{\bf \overline{F}_i}\chainedlink{\bf \overline{F}_o}{\overline{F}_o}\chainedlink{cxt}{cxt}
\chainedlink{\underline{C}_i}{\bf \underline{C}_i}\chainedlink{\bf \underline{C}_o}{\underline{C}_o}
\chainedlink{\underline{G}_i}{\bf \underline{G}_i}\chainedlink{\bf \underline{G}_o}{\underline{G}_o}
\chainedlink{\hat{F}_i}{\bf \hat{F}_i}\chainedlink{\bf \hat{F}_o}{\hat{F}_o}\chainedlink{p_1}{p_1} 
 \chainedlink{\tilde{T}_i}{\bf \tilde{T}_i}\chainedlink{\bf \tilde{T}_o}{\tilde{T}_o}
  \chainedlink{p_2}{p_2}\chainedlink{p_3}{p_3}\chainedlink{p_4}{p_4} \chainedlink{\tilde{G}_i}{\bf \tilde{G}_i}\chainedlink{\bf \tilde{G}_o}{\tilde{G}_o} \chainend{\silent}
\end{array}
\]
